# Web-enabled and Cross-platform SAM via Shiny

First make sure you have a very recent version of R or RStudio.

Next install required packages. Cut and paste what's below in an R session.

```{r}
install.packages(c("matrixStats", "GSA", "shiny", "shinyFiles", "openxlsx"))
source("http://bioconductor.org/biocLite.R")
biocLite("impute")
```
You only need to do this once.

Then, install the current version of the package, after removing any
older versions you may have already installed. _Later, when this
package makes it to CRAN, you will install it the usual way_.

```{r}
if (! ("devtools" %in% installed.packages()) ) install.packages("devtools")
install_github("bnaras/samr")
runSAM()
```

That will bring up a browser window with a user interface. More
details are provided in the manual `sam.pdf` in this directory

Please post to the group regarding any issues. This will help us
ensure we have all the kinks ironed out before merging the code into
the next version of the `samr` package.

Note that users should use Firefox or Chrome as the _default_browser
on Windows: IE will not work.

Thank you,
Michael Seo
